\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-07 paper/paper 2/dc-2015.tex
2.3

If constraint types are expressible in DL, associated constraining elements are formally based on DL constructs like concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$), equality (=), and inequality ($\ne$). In case constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse terms from SPARQL (e.g., \emph{regex}) and XML Schema constraining facets (e.g., \emph{minInclusive}). For some constraint types like \emph{cardinality restrictions}, it is more intuitive to reuse the DL terms $\geq$ and $\leq$ as constraining elements instead of, for instance, \emph{minimum qualified cardinality restriction}. We provide a complete list of all constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.

>>>>

If constraint types are expressible in DL, associated constraining elements are formally based on DL constructs like concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$), equality (=), and inequality ($\ne$). In case constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse widely known terms from SPARQL (e.g., \emph{regex}) or XML Schema (e.g., \emph{minInclusive}) as constraining elements. For some constraint types like \emph{minimum qualified cardinality restrictions (R-75)}, it is more intuitive and concise to directly apply DL constructs like the \emph{at-least restriction} ($\geq$) as constraining elements. We provide a complete list of all constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.
